Sardines only end-to-end atlantisom test

### 2019-06-03 SardinesOnlyatlantisom2SStest.Rmd
add ss survey
add sampling and plots

```{r trueB-N}

@@

Get true population age composition. Now we go to single species to speed things up.

```{r true-B-N}

@@

Get true population length comp and weight at age

```{r true-comps}

>>>>

```{r trueB-N, eval=FALSE}

@@

Plot true biomass and numbers for "sardines."

```{r plot-true-B-N}

trueB <- readRDS(file.path(d.name, paste0(scenario.name,"surveyBcensus.rds")))

trueB_ss <- trueB %>%
  filter(species==species_ss)

plotB <-ggplot() +
  geom_line(data=trueB_ss, aes(x=time/stepperyr,y=atoutput, color="survey census N"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotB +
  facet_wrap(~species, scales="free")

trueN <- readRDS(file.path(d.name, paste0(scenario.name,"surveyNcensus.rds")))

trueN_ss <- trueN %>%
  filter(species==species_ss)

plotN <-ggplot() +
  geom_line(data=trueN_ss, aes(x=time/stepperyr,y=atoutput, color="survey census N"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotN +
  facet_wrap(~species, scales="free")

@@

Get true population age comp, length comp, and weight at age. Now we go to single species to speed things up.

```{r true-comps, warning=FALSE, message=FALSE}

# wrap these individual calls into a function
survey_N_ss <- create_survey(dat = truth$nums,
                                 time = timeall,
                                 species = species_ss,
                                 boxes = boxall,
                                 effic = effic1,
                                 selex = selex1)

# apply default sample fish to get numbers, effNhigh samples all, see census_spec
numssshigh <- sample_fish(survey_N_ss, effNhigh)

# save age comps
saveRDS(numssshigh, file.path(d.name, paste0(scenario.name, "natage_census_sard.rds")))

# aggregate true resn per survey design
aggresnss <- aggregateDensityData(dat = truth$resn,
                                 time = timeall,
                                 species = species_ss,
                                 boxes = boxall)

# aggregate true structn per survey design
aggstructnss <- aggregateDensityData(dat = truth$structn,
                                 time = timeall,
                                 species = species_ss,
                                 boxes = boxall)

#dont sample these, just aggregate them using median
structnss <- sample_fish(aggstructnss, effNhigh, sample = FALSE)

resnss <-  sample_fish(aggresnss, effNhigh, sample = FALSE)

# this function does the length sampling and also weight at age
length_census_ss <- calc_age2length(structn = structnss,
                                 resn = resnss,
                                 nums = numssshigh,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

#save for later use, takes a long time to generate
saveRDS(length_census_ss, file.path(d.name, paste0(scenario.name, "lengthwt_census_sard.rds")))

Plot some of the age, length comps, and wtatage

```{r plot-true-agecomps}

Natage <- readRDS(file.path(d.name, paste0(scenario.name, "natage_census_sard.rds")))

Natageplot <- ggplot(Natage, aes(x=agecl, y=atoutput)) +
  geom_point() +
  theme_tufte() +
  labs(subtitle = paste(scenario.name,
                        Natage$species))

Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 1, scales="free")
Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 2, scales="free")
Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 3, scales="free")
Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 4, scales="free")

```{r lf-plot}

lengthwt_census_ss <- readRDS(file.path(d.name, paste0(scenario.name, "lengthwt_census_sard.rds")))

len <- lengthwt_census_ss$natlength

lfplot <- ggplot(len, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name,
                        len$species))

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")

```{r wtage-plot}

wageplot <- ggplot(lengthwt_census_ss$muweight, aes(agecl, atoutput)) +
  geom_point(aes(colour = time)) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  scale_x_discrete(limits=c(1:10)) +
  xlab("age class") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste(scenario.name))

wageplot + facet_wrap(c("species"), scales="free_y")
